Anonymous provision of local services via blockchain

### 2022-02-22 access.tex
update access tex

We propose a framework for coordingating local anonymous service
provision. Our proposal uses blockchain for both anonymous payments and
proofs of existence (so called Message Board), and content addressable
network (e.g.~IPFS) for results delivery.

@@

People willing to take business action that may be risky or not yet
fully legistlated, may be willing to receive the rist estimation and
prediction of possible repercussions of such action.

By exposing our identity to the lawer, we trust that he won't use that
information for harmful actions.

@@

\begin{itemize}
\item Anonimity:
throughout the whole transaction the customer stays anonymous to all external observers.
\item Fairness:
at each step of the protocol, both parties are incentivised to act accordingly to the protocol; otherwise the misbehaving party ends up in worst position.
\item Dispute resolution: at each step of the protocol the customer can open a dispute win the case iff the SP misbehaved.
\item TTP-less: our protocol does not rely on trusted-third party to conduct transactions in fairly manner. Only in case of dispute the centralized justice is invlolved (the justice decentralisation is discussed in {[}{[}Future Work{]}{]}).
\item Physical materials: our protocol allows providing not only
  digital but also physical materials to the service provider.
\end{itemize}

Some authors have proposed blockchain-based fair-exchange systems that
could be adapted to service provision; however, to our best knowledge we
are the first to propose a system that satisfy all five properties
stated above. Especially anonimity and physical materials delivery, are
properties that were rarely addressed together, and if so, the protocol
based on TTP, and strong and impractial assumptions on banking system
\cite{birjoveanu2015anonymity}, or didn't address the of conflict
between parties \cite{altawy2017lelantos}.

@@

Authors of \cite{birjoveanu2015anonymity} proposed a
fair-exchange of physical product and electronic payment protocol that
guarantee both customer and merchant anonymity. They achieve it by
introducing online trusted third party that validate coins and provide
fair exchange guarantees.

@@

Themis\cite{meng2019themis} is a fair-exchange
protocol, which uses blockchain instead of TTP. It provide escrow
services for secure exchanging between cryptocurrencies and digital
goods.

@@

Lelanros\cite{altawy2017lelantos} is a blockchain-based anonymous
physical delivery system. The anonymity is achieved by employing ToR's
onion routing to connect physical delivery providers. The whole route
from merchant to customer is split into multiple steps, and each step is
undertaken by different randomly selected delivery provider. As long as
the develiery providers does no collude, mechant can not learn both
identity and destination address of the customer.

@@

Themis \cite{meng2019themis} besides providing fair-exchange protocol,
also offers a semi-autonomous decentralised dispute resolution system,
which comply with the web3 postulates of decentralised web. Themis
resolve disputes by set of voluntary anonymous mediators participating
in a voting and deciding whether a party misbehaved. The honesty of
mediators is achieved by the monetary incentivization and reputation
system.

Kleros \cite{lesaege2018kleros} is a smart contract deployed on
Ethereum platform that mimics in decentralised and autonomous way how
court works in real life. In Kleros, every process of a dispute like
gathering evidences, selecting jurors, rewarding the winning party is if
automated by a set of smart contracts. Simillar to Themis, the honesty
of the agents voting in a case is achieved by game-theoretical economic
incentives.

@@

Possible directions toward semi-autonomous decentralised resolution
system are discussed in {[}{[}anonser/Future Work{]}{]}.

\subsection{Proof to justice}
In case of dispute the customer can proof to the justice (police, court,
etc.) evidences that convinces the justice about the honesty of customer
and misbehaviour of SP. The reason why the SP can not start a dispute is
that the customer is anonymous, and therefore there is no personal
information to start a dispute aginst. To mitigate this issue the SP is
always in advantaged postition, so that he has no reason to start a
dispute. The idea described firther in {[}{[}Fairness analysis{]}{]}.

@@

The second proof depend on the cryptocurrency implementation and is
discussed further in section {[}{[}Payment for services{]}{]}.

In case the SP has fulfulled the transaction and provide the results,
but the customer unjustly start a dispute, the SP is secured by the
proof-of-provision (PoP) he's published on the message board
({[}{[}Message Board{]}{]}).

@@

\item
  \(\mathrm{cid}\) - content identifier as specified in {[}{[}Storage
  Network{]}{]}.
\item
  \(\mathrm{nonce}\) - the value uniquely identifying the transaction
  previosuly generated in PoD.
\item
  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
  non-repudiation.
\end{itemize}

@@

Depending on the context the platform of achieving it is called bulletin
board \cite{achenbach2015improved} or message board
\cite{hinarejos2019solution} or trusted timestamping
\cite{gipp2015decentralized}. In this work we call it Message Board.

@@

Bitcoin introduced a way of decentralizing not only the currency system,
but also other similary working centralized trusted third parties
including the Message Board.

We let keep the protocol general enough to let the implementator use any
existing technology to provide Message Board service, with the
assumption that it's decentralised and supports subscribing for the
upcoming proofs from particular address.

\subsection{Pseudo-anonymous vs anonymous blockchain}
Privacy is a concept used in almost all kinds of social sciences like
philosophy, psychology, sociology, and legal. The multidisciplinary
nature leads to ambigous definitions\cite{smith2011information}. For
the purpose of our work we rely on more concrete definitions,
i.e.~confidentality and anonimity.

@@

Anonymity is a the ability to hide one identity from others. More
precisely, the unability to correlate actions performed within the sytem
to the identity of the user. Or we can say, that the system guarantee
anonimity if for all observers the actions are equally likely to be
associated with any user of the system. However, anonimity is a spectrum
rather than dichotomous classification. One method of quantifying level
of anonymity is proposed in k-anonymity \cite{sweeney2002k}. It measure
the user's anonymity by the number of other users from whom the user can
not be distinguished. Concreatly, the user is \emph{k}-anonymous if his
actions are equaly likely associated with \emph{k}-1 other users. The
larger \emph{k}, the higher anonimity.

The cryptocurrencies that natively support anonymous transactions are
Monero \cite{van2013cryptonote} (via Bulletproofs
\cite{Bulletpr14, bunz2018bulletproofs}) and ZCash
\cite{sasson2014zerocash} (via zk-SNARK \cite{ben2013snarks}), Grin
\cite{fuchsbauer2019aggregate} (via Mimblewimble \cite{httpsdow19}).

There are also techniques that can be deployed on non-anonymous
blockchains, the so called mixers: Ethereum's Tornado
Cash\cite{pertsev2019tornado}, Bitcoin's Wasabi\cite{WasabiWa56} (uses
CoinJoin \cite{CoinJoin41}) that literaly gather together users into an
``anonimimity set'', which then collude together in order to launder the
transactions, in such a way that to a observer the likelyhood of the
sender of each transaction was equiprobable for any user from the
anonimity set.

Some systems guarantee pseudonomity rather than anonimity. Pseudonomity,
allows uses to hide their real identity behind the pseudonim. Despite
the whole system is transparent and allows linking actions to one
identity, the system is considered anonymous as long as the link between
pseudonym and real identity is secret. This assumption is hard to
satisfy in practice, as the KYC (Know You Customer) and AML (Anti Money
Laundering) regulations require users to reveal their real identity on
most of the cryptocurrencies exchanges. This makes the anonymity of the
user dependent on the security of the IT system. Moreover, some
correlations can be infered merely by the analysis of transactions
\cite{androulaki2013evaluating, ober2013structure}. Most of the
blockchains, including Bitcoin and Ethereum achieve this kind of
pseudonimity.

@@

\subsection{Payment for services}
Transactions between customers and SP have to be somehow pegged in order
to prevent proving one payment for multiple transactions. In other
words, we need some way to uniquely link particular payment with the
transaction it pays for.

@@

\subsection{Storage network}
Once the SP finish its service, he has to provide the results to the
customer. The most natural approach would to be send the results via
email of decidated platform. However, since the customer wants to stay
anonymous, he don't want to expose his email address nor IP address.
Moreover, in case of dispute the SP should be able to prove that the
results have been provided before the deadline.

One approach would be to post the results into a blockchain. Yet,
storing data on a blockchain is very expensive. The most common
workaround
(\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95})
is to publish the data to the IPFS \cite{benet2014ipfs}---a content
adressable peer-to-peer storage network---and publish to a blockchain
just a content identifier (cid) that uniquely points to the content
stored on the IPFS.

@@

\subsection{Separation of concerns}
We could use one blockchain to achieve all of these three roles: (i)
Anonymous payments; (ii) Message Board; (iii) Storage network.

As the Message board could be achieved by most of the blockchanis, the
anonymous payments isn't so prevalent, and provable storage network is a
functionality of a few specialized blockchains.

@@

\item Anonymous payments: Monero \cite{van2013cryptonote}, ZCash
  \cite{sasson2014zerocash}, Grin \cite{fuchsbauer2019aggregate},
  Tornado Cash \cite{pertsev2019tornado}.
\item Message Board: Stampery \cite{de2016stampery}, Proof of Existence
  \cite{proofofexistence} (Bitcoin blockchain), Chainpoint
  \cite{Chainpoi39} (Bitcoin blockchain), or any other blockchain that
  supports attaching extra data along the transaction.
\item Storage network: IPFS \cite{benet2014ipfs}, Filecoin
  \cite{benetfilecoin} (runs on top of IPFS), or Ethereum's
  Swarm\cite{swarmwhi49}.
\end{enumerate}

@@

\item
  SPs accept packages from unknown customers and give them back
  confirmation of acceptance (to stick with convention we call it
  Proof-of-Delivery).
\item
  SPs accept payment for services via anonymous cryptocurrencies like
  Monero, Grin or ZCash as described in {[}{[}Payment for
  services{]}{]}.
\item
  Justice accepts as a evidence in dispute proof of payment of
  cryptocurrencies as described in {[}{[}Proof to Justice{]}{]}.
\end{itemize}

\subsection{Protocol description}

@@

\[\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{key})\]

@@

\item
  \(\mathrm{materials}\) - are the materials needed to provide the
  service on. For example, sample of urine, blood, stool, saliva; legal
  documents, CDs, mails, photos, bank statement, or any other kind of
  evidence depending on the service.
\item
  \(\mathrm{key}\) - symmetric key used to encrypt and decrypt the
  results.
\end{itemize}

@@

\[\mathrm{PoD} \equiv (\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})\]

@@

@@

\item
  \(\mathrm{cid}\) - content identifier as specified in {[}{[}Storage
  Network{]}{]}.
\item
  \(\mathrm{nonce}\) - the value uniquely identifying the transaction
  previosuly generated in PoD.
\item
  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
  non-repudiation.
\end{itemize}

@@

Payment attestation proves that the customer did the payment. Since the
evidences depends on the particular blockchain (see Section
{[}{[}Payment for services{]}{]}). We refer to them symbollicaly as
\(attestation\).

@@

In return, the SP issue an Proof-of-Delivery (POD) confirmation. The
confirmation encompasses timestamp, invoice (see section {[}{[}Payment
for services{]}{]}), and signature.

@@

Having POD, SP can not reject receiving the package. At this point the
customer should pay for the invoice according to selected cryptocurrency
system (see section {[}{[}Payment for services{]}{]}).

@@

\item
  Both parties start from neutral position (•).
\item
  Both parties, by completing a transaction, end up in advantaged
  positions (+). In other words, they have intrinsic motivation to
  initialise the transaction.
\item
  We assume the steps of the protocol to be atomic, there are no
  intermediate steps.
\item
  Repeating the first step starts new transaction. Repeating any other
  step is considered abnormal and gets ignored. For example paying for
  the invoice twice does not cause any effect on the curse of protocol.
\item
  Once published, the results are avaiable to the customer in the
  content storage. The idea of guaranteeing it cryptographically is
  discussed in {[}{[}Future Work{]}{]}.
\item
  The protocol can go only forward, there is no way of revert any
  action.
\item
  Losing the dispute leads to punishment that is greater than any
  reward, which leads to disadvantaged position. Hence, the rational
  customer won't start a dispute that he is not sure to win.
\item
  Winning the dispute leads to neutral position (•)
\item
  Both the customer and the SP are rational (selfish). They always
  prefer go from worst position to better position, but also risk
  temporary worst position in favour for later better position iff it's
  assured that they won't stuck in worst position.
\end{itemize}

@@

\section{Future work}
\subsection{Justice}\label{justice}

Justice is the one biggest obstacle in achieving system that is complied
with web3 manifests.

The possible directions for mitigation of such issue are to either (1)
replace Justice with decentralised autonomous organisations (DAO) like
proposed in Themis\cite{meng2019themis} or
Kleros\cite{lesaege2018kleros}; or (2) make it infeasible to provide
incorrect results.

@@

The second approach is more philosophical and visionary. Suppose that
the service we are undertaking is fully computable. Then, it would be
possible by employing proofs of correctness of
computations\cite{ben2013snarks} to enforce that only correct
computations (hence correct services) are accepted. To do so the whole
service examination would have to be computable, which is hard to
achieve in settings where physical materials (like blood) are examined.
Concretely, the problem canes down to ``How to digitally represent
blood''. If we could represent urine, blood, saliva, or any other
physical material in binary format, and let the customer to take a
sample, discrete it and send it to the SP by himself, then the whole
chain of integrity could be ensured. Therefore, wrong service provision
would be infeasible.

@@

Currently, the SP has to publish the results into a p2p content storage
network (IPFS). The problem is that, nothing prevent such SP to publish
the content, receive the content identifier (cid), and immediately after
remove it from from it's local storage. In case of dispute the SP can
upload the content again, proving its availability. The SP has no
motivation to proceed with this kind of misbehaviour, other than puting
the customer in disadvantaged position caused by the lost dispute. We see
possible prevention of this misbehaviour by the usage of Filecoin---an
incentive layer on top of IPFS that guarantee the content availability
via economic incentivisations Filecoin\cite{benetfilecoin}. With the
help of Filecoin, the SP would be obligated to create a Filecoin deal
that guarantee the results availability until the deadline of the
transaction. Moreover, since Filecoin is a blockchain by itself, it
could play both roles of Message Board and Storage Network.

>>>>

We propose a framework for coordingating local anonymous service
provision. Our proposal uses blockchain for both anonymous payments and
proofs of existence (so called message board), and content addressable
network (e.g.~IPFS) for results delivery.

@@

People willing to take business action that may be risky or not yet fully legislated, may be willing to receive the risk estimation and prediction of possible repercussions of such action.

By exposing our identity to the lawyer, we trust that he won't use that
information for harmful actions.

@@

\begin{itemize}
\item Anonimity:
throughout the whole transaction the customer stays anonymous to all external observers.
\item Fairness:
at each step of the protocol, both parties are incentivised to act accordingly to the protocol; otherwise the misbehaving party ends up in worst position.
\item Dispute resolution: at each step of the protocol the customer can open a dispute win the case iff the SP misbehaved.
\item TTP-less: our protocol does not rely on trusted-third party to conduct transactions in fairly manner. Only in case of dispute the centralized justice is invlolved (the justice decentralisation is discussed in section ~\ref{future-work}.
\item Physical materials: our protocol allows providing not only
  digital but also physical materials to the service provider.
\end{itemize}

Some authors have proposed blockchain-based fair-exchange systems that
could be adapted to service provision; however, to our best knowledge we
are the first to propose a system that satisfy all five properties
stated above. Especially anonimity and physical materials delivery, are
properties that were rarely addressed together, and if so, the protocol
based on TTP, and strong and impractial assumptions on banking system~\cite{birjoveanu2015anonymity}, or didn't address the of conflict
between parties~\cite{altawy2017lelantos}.

@@

Authors of~\cite{birjoveanu2015anonymity} proposed a
fair-exchange of physical product and electronic payment protocol that
guarantee both customer and merchant anonymity. They achieve it by
introducing online trusted third party that validate coins and provide
fair exchange guarantees.

@@

Themis~\cite{meng2019themis} is a fair-exchange
protocol, which uses blockchain instead of TTP. It provide escrow
services for secure exchanging between cryptocurrencies and digital
goods.

@@

Lelanros~\cite{altawy2017lelantos} is a blockchain-based anonymous
physical delivery system. The anonymity is achieved by employing ToR's
onion routing to connect physical delivery providers. The whole route
from merchant to customer is split into multiple steps, and each step is
undertaken by different randomly selected delivery provider. As long as
the develiery providers does no collude, mechant can not learn both
identity and destination address of the customer.

@@

Themis~\cite{meng2019themis} besides providing fair-exchange protocol,
also offers a semi-autonomous decentralised dispute resolution system,
which comply with the web3 postulates of decentralised web. Themis
resolve disputes by set of voluntary anonymous mediators participating
in a voting and deciding whether a party misbehaved. The honesty of
mediators is achieved by the monetary incentivization and reputation
system.

Kleros~\cite{lesaege2018kleros} is a smart contract deployed on
Ethereum platform that mimics in decentralised and autonomous way how
court works in real life. In Kleros, every process of a dispute like
gathering evidences, selecting jurors, rewarding the winning party is if
automated by a set of smart contracts. Simillar to Themis, the honesty
of the agents voting in a case is achieved by game-theoretical economic
incentives.

@@

Possible directions toward semi-autonomous decentralised resolution
system are discussed in section ~\ref{future-work}.

\subsection{Proof to justice}\label{proof-of-justice}
In case of dispute the customer can proof to the justice (police, court,
etc.) evidences that convinces the justice about the honesty of customer
and misbehaviour of SP. The reason why the SP can not start a dispute is
that the customer is anonymous, and therefore there is no personal
information to start a dispute against. To mitigate this issue the SP is
always in advantaged postition, so that he has no reason to start a
dispute. The idea described further in section ~\ref{future-work}.

@@

The second proof depend on the cryptocurrency implementation and is
discussed further section~\ref{payment-for-services}.

In case the SP has fulfilled the transaction and provide the results,
but the customer unjustly start a dispute, the SP is secured by the
proof of provision (PoP) he has published on the message board (described in section ~\ref{message-board}.

@@

\item
  \(\mathrm{cid}\) - content identifier as specified in section ~\ref{storage-network}.
\item
  \(\mathrm{nonce}\) - the value uniquely identifying the transaction
  previosuly generated in PoD.
\item
  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
  non-repudiation.
\end{itemize}

@@

Depending on the context the platform of achieving it is called bulletin
board~\cite{achenbach2015improved} or message board~\cite{hinarejos2019solution} or trusted timestamping~\cite{gipp2015decentralized}. In this work we call it message board.

@@

Bitcoin introduced a way of decentralizing not only the currency system,
but also other similary working centralized trusted third parties
including the message board.

We let keep the protocol general enough to let the implementator use any
existing technology to provide message board service, with the
assumption that it's decentralised and supports subscribing for the
upcoming proofs from particular address.

\subsection{Pseudo-anonymous vs anonymous blockchain}
Privacy is a concept used in almost all kinds of social sciences like
philosophy, psychology, sociology, and legal. The multidisciplinary
nature leads to ambigous definitions~\cite{smith2011information}. For
the purpose of our work we rely on more concrete definitions,
i.e.~confidentality and anonimity.

@@

Anonymity is a the ability to hide one identity from others. More
precisely, the unability to correlate actions performed within the sytem
to the identity of the user. Or we can say, that the system guarantee
anonimity if for all observers the actions are equally likely to be
associated with any user of the system. However, anonimity is a spectrum
rather than dichotomous classification. One method of quantifying level
of anonymity is proposed in \textit{k}-anonymity~\cite{sweeney2002k}. It measure
the user's anonymity by the number of other users from whom the user can
not be distinguished. Concretely, the user is \textit{k}-anonymous if his
actions are equally likely associated with \textit{k}-1 other users. The
larger \textit{k}, the higher anonymity.

The cryptocurrencies that natively support anonymous transactions are
Monero~\cite{van2013cryptonote} (via Bulletproofs~\cite{Bulletpr14, bunz2018bulletproofs}) and ZCash~\cite{sasson2014zerocash} (via zk-SNARK~\cite{ben2013snarks}), Grin~\cite{fuchsbauer2019aggregate} (via Mimblewimble~\cite{httpsdow19}).

There are also techniques that can be deployed on non-anonymous
blockchains, the so called mixers: Ethereum's Tornado
Cash\cite{pertsev2019tornado}, Bitcoin's Wasabi\cite{WasabiWa56} (uses
CoinJoin \cite{CoinJoin41}) that literaly gather together users into an
\textit{anonymity set}, which then collude together in order to launder the
transactions, in such a way that to a observer the likelihood of the
sender of each transaction was equiprobable for any user from the
anonymity set.

Some systems guarantee pseudonomity rather than anonymity. Pseudonomity,
allows uses to hide their real identity behind the pseudonim. Despite
the whole system is transparent and allows linking actions to one
identity, the system is considered anonymous as long as the link between
pseudonym and real identity is secret. This assumption is hard to
satisfy in practice, as the KYC (Know You Customer) and AML (Anti Money
Laundering) regulations require users to reveal their real identity on
most of the cryptocurrencies exchanges. This makes the anonymity of the
user dependent on the security of the IT system. Moreover, some
correlations can be infered merely by the analysis of transactions
\cite{androulaki2013evaluating, ober2013structure}. Most of the
blockchains, including Bitcoin and Ethereum achieve this kind of
pseudonimity.

@@

\subsection{Payment for services}\label{payment-for-services}
Transactions between customers and SP have to be somehow pegged in order
to prevent proving one payment for multiple transactions. In other
words, we need some way to uniquely link particular payment with the
transaction it pays for.

@@

\subsection{Storage network}\label{storage-network}
Once the SP finish its service, he has to provide the results to the
customer. The most natural approach would to be send the results via
email of decidated platform. However, since the customer wants to stay
anonymous, he don't want to expose his email address nor IP address.
Moreover, in case of dispute the SP should be able to prove that the
results have been provided before the deadline.

One approach would be to post the results into a blockchain. Yet,
storing data on a blockchain is very expensive. The most common
workaround
(\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95})
is to publish the data to the IPFS \cite{benet2014ipfs}—a content
adressable peer-to-peer storage network—and publish to a blockchain
just a content identifier (cid) that uniquely points to the content
stored on the IPFS.

@@

\subsection{Separation of concerns}
We could use one blockchain to achieve all of these three roles: (i)
anonymous payments; (ii) message board; (iii) storage network.

As the message board could be achieved by most of the blockchanis, the
anonymous payments isn't so prevalent, and provable storage network is a
functionality of a few specialized blockchains.

@@

\item Anonymous payments: Monero \cite{van2013cryptonote}, ZCash
  \cite{sasson2014zerocash}, Grin \cite{fuchsbauer2019aggregate},
  Tornado Cash \cite{pertsev2019tornado}.
\item Message board: Stampery \cite{de2016stampery}, Proof of Existence
  \cite{proofofexistence} (Bitcoin blockchain), Chainpoint
  \cite{Chainpoi39} (Bitcoin blockchain), or any other blockchain that
  supports attaching extra data along the transaction.
\item Storage network: IPFS \cite{benet2014ipfs}, Filecoin
  \cite{benetfilecoin} (runs on top of IPFS), or Ethereum's
  Swarm\cite{swarmwhi49}.
\end{enumerate}

@@

\item
  SPs accept packages from unknown customers and give them back
  confirmation of acceptance (to stick with convention we call it
  Proof-of-Delivery).
\item
  SPs accept payment for services via anonymous cryptocurrencies like
  Monero, Grin or ZCash as described in section ~\ref{payment-for-services}.
\item
  Justice accepts as a evidence in dispute proof of payment of
  cryptocurrencies as described in section~\ref{proof-of-justice}.
\end{itemize}

@@

$$\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{key})$$

@@

\item $\mathrm{materials}$ - are the materials needed to provide the
  service on. For example, sample of urine, blood, stool, saliva; legal
  documents, CDs, mails, photos, bank statement, or any other kind of
  evidence depending on the service.
\item $\mathrm{key}$ - symmetric key used to encrypt and decrypt the
  results.
\end{itemize}

@@

$$\mathrm{PoD} \equiv (\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})$$

@@

\item $\mathrm{T}_\mathrm{issue}$ - time at which the PoD is issued.
\item
  $\mathrm{T}_\mathrm{pay}$ - deadline to pay for the transaction.
\item
  $\mathrm{T}_\mathrm{provide}$ - deadline to provide the service
  results.
\item $\mathrm{nonce}$ - randomly generated number uniquely identifying
  the transaction.
\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing
  non-repudiation.
\end{itemize}

@@

\item
  \(\mathrm{cid}\) - content identifier as specified in ~\ref{storage-network}.
\item
  \(\mathrm{nonce}\) - the value uniquely identifying the transaction
  previosuly generated in PoD.
\item
  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
  non-repudiation.
\end{itemize}

@@

Payment attestation proves that the customer did the payment. Since the
evidences depends on the particular blockchain (see section ~\ref{payment-for-services}). We refer to them symbollicaly as
\(attestation\).

@@

In return, the SP issue an Proof-of-Delivery (POD) confirmation. The
confirmation encompasses timestamp, invoice (see section \ref{payment-for-services}), and signature.

@@

Having POD, SP can not reject receiving the package. At this point the
customer should pay for the invoice according to selected cryptocurrency
system (see section~\ref{payment-for-services}).

@@

\item
  Both parties start from neutral position (•).
\item
  Both parties, by completing a transaction, end up in advantaged
  positions (+). In other words, they have intrinsic motivation to
  initialise the transaction.
\item
  We assume the steps of the protocol to be atomic, there are no
  intermediate steps.
\item
  Repeating the first step starts new transaction. Repeating any other
  step is considered abnormal and gets ignored. For example paying for
  the invoice twice does not cause any effect on the curse of protocol.
\item
  Once published, the results are available to the customer in the
  content storage. The idea of guaranteeing it cryptographically is
  discussed in section ~\ref{future-work}.
\item
  The protocol can go only forward, there is no way of revert any
  action.
\item
  Losing the dispute leads to punishment that is greater than any
  reward, which leads to disadvantaged position. Hence, the rational
  customer won't start a dispute that he is not sure to win.
\item
  Winning the dispute leads to neutral position (•)
\item
  Both the customer and the SP are rational (selfish). They always
  prefer go from worst position to better position, but also risk
  temporary worst position in favour for later better position iff it's
  assured that they won't stuck in worst position.
\end{itemize}

@@

\section{Future work}\label{future-work}
\subsection{Justice}\label{justice}

Justice is the one biggest obstacle in achieving system that complies with Web3 postulates~\cite{Web3Wiki71}.

The possible directions for mitigation of such issue are to either (1)
replace Justice with decentralised autonomous organisations (DAO) like
proposed in Themis~\cite{meng2019themis} or
Kleros~\cite{lesaege2018kleros}; or (2) make it infeasible to provide
incorrect results.

@@

The second approach is more philosophical and visionary. Suppose that
the service we are undertaking is fully computable. Then, it would be
possible by employing proofs of correctness of
computations~\cite{ben2013snarks} to enforce that only correct
computations (hence correct services) are accepted. To do so the whole
service examination would have to be computable, which is hard to
achieve in settings where physical materials (like blood) are examined.
Concretely, the problem canes down to ``How to digitally represent
blood''. If we could represent urine, blood, saliva, or any other
physical material in binary format, and let the customer to take a
sample, discrete it and send it to the SP by himself, then the whole
chain of integrity could be ensured. Therefore, wrong service provision
would be infeasible.

@@

Currently, the SP has to publish the results into a p2p content storage
network (IPFS). The problem is that, nothing prevent such SP to publish
the content, receive the content identifier (cid), and immediately after
remove it from from it's local storage. In case of dispute the SP can
upload the content again, proving its availability. The SP has no
motivation to proceed with this kind of misbehaviour, other than puting
the customer in disadvantaged position caused by the lost dispute. We see
possible prevention of this misbehaviour by the usage of Filecoin---an
incentive layer on top of IPFS that guarantee the content availability
via economic incentivisations Filecoin~\cite{benetfilecoin}. With the
help of Filecoin, the SP would be obligated to create a Filecoin deal
that guarantee the results availability until the deadline of the
transaction. Moreover, since Filecoin is a blockchain by itself, it
could play both roles of message board and Storage Network.
